A Survey of Sterile Neutrinos

### 2015-04-15 p3_505/paper/paper3.tex
Finished my sections, pasted in pings

\documentclass[aps,prd,twocolumn,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{epsfig}
\usepackage{listings}
\usepackage[hidelinks,hyperfootnotes=false,bookmarks=false]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{verbatim}
\usepackage{float}
\begin{document}
\title{A Survey of Sterile Neutrinos}
\author{Douglas Davis}
\author{Matthew Epland}
\author{Justin Raybern}
\author{Pingchuan Zhao}
\affiliation{Department of Physics, Duke University, Durham, NC 27707, USA}
\date{\today}
\begin{abstract}
  xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxx
\end{abstract}\maketitle
\section{Theory}
\label{sec:theory}
\subsection{Theory Ping}

@@

\subsubsection{Super-Kamiokande}
The Super-Kamiokande experiment is a 22.5 kton water Cherenkov detector that looks at atmospheric neutrino oscillations. Their latest sterile neutrino analysis~\cite{SuperK} used a sterile vacuum fit to put limits on the mixing between $\nu_{\mu}$ and a sterile neutrino $\nu_4$, parameterized by $\left|U_{\mu 4}\right|^2 \approx sin^2 \theta_{24}$, Figure~\ref{fig:SuperK}. Super-K can not measure $\Delta m^{2}_{41}$ in this analysis however, so when comparing to MiniBooNE the Super-K result is just a straight line. The Super-K result is is consistent with the MiniBooNE exclusion, providing verification on at least part of the MiniBooNE excluded region.

@@

\subsubsection{Daya Bay}

~\cite{DayaBay}

\begin{figure}[H]
 \centering
 \includegraphics[width=1\columnwidth]{../figures/daya1.pdf}
 \caption{Daya Bay sterile neutrino exclusion limits~\cite{DayaBay}. TODODESCRIPTIONHERE}
 \label{fig:DayaBay}
\end{figure}

>>>>

\documentclass[aps,prd,twocolumn,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{epsfig}
\usepackage{listings}
\usepackage[hidelinks,hyperfootnotes=false,bookmarks=false]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{verbatim}
\usepackage{float}
\begin{document}
\title{A Survey of Sterile Neutrinos}
\author{Douglas Davis}
\author{Matthew Epland}
\author{Justin Raybern}
\author{Pingchuan Zhao}
\affiliation{Department of Physics, Duke University, Durham, NC 27707, USA}
\date{\today}
\begin{abstract}
  xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx xxxxxxxxxxxxxxxxxxxxx
\end{abstract}\maketitle
\section{Theory}
\label{sec:theory}
xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx
\subsection{Theory}
%ping
A neutrino is an electrically neutral, weakly interacting elementary particle with half integer spin. There are generations of neutrinos: electron-neutrino, muon-neutrino and tau-neutrino. It is first indicated from beta decay spectrum. From the experiment of radioactive decay, the outgoing electron energy varies differently, hence it is not a 2-body decay, but actually a 3-body decay. Pauli first called that small, neutral charge particle neutrino. Soon, this explanation is accepted among physicists and after a few years, anti-neutrinos is found from inverse beta decay.

In the Standard Model, there are three generations of neutrinos. However, the Lagrangian has no neutrino mass term, giving neutrinos have exactly zero mass. Also, neutrinos and anti-neutrinos are distinct, separating by helicity. From experiment measurements, neutrinos always have left helicity and anti-neutrinos with right helicity. Neutrinos couple with W,Z bosons only in this model~\cite{ping1}.

Although the Standard Model is exceedingly successful in explaining the interactions among fundamental particles, it can not be the ultimate theory, since it does not give explanation on gravity, dark matter, neutrino mass and neutrino oscillation. In 1960s, the solar neutrino experiment first indicates that there is a change of flavor when neutrinos traveling. This is also the first evidence that shows neutrinos have some mass. By using the detector Kamiokande and later the upgraded version, Super Kamiokande, they observe the flavor changes not only from solar neutrinos but also long-baseline reactor neutrinos.

Starting in the late 1960s, there is a discrepancy using Standard Model to give explanations to neutrinos arriving from the sun~\cite{ping2}. The observed electron neutrinos are only between one third to one half of what Standard Model predicts. This problem remains unsolved until almost 30 years later as the observation of neutrino oscillation, which give a perfect explanation on solar neutrino problem. Since the neutrinos are changing flavors when traveling, the fraction of electron has changed to other flavors, and the fraction can be calculated from the mixing angles of oscillations. The mixing angles now have all been experimentally determined, with the last one $\theta_{13}$ found in 2012 in Daya Bay experiment~\cite{ping3}. However, the mixing angles and oscillation experiment only gives the relative mass between different flavors of neutrinos, this can not give the absolute mass of neutrinos. Hence the neutrino mass is crucial problem to understand nowadays. Neutrinos may be Majorana particles which is that they are their own antiparticles. If this is true, then not only the absolute mass of neutrinos can be observed, but also it explains why after the universe evolves, the matter dominates over anti-matter~\cite{ping4}.

%The neutrinoless double beta decay experiment are very similar to dark matter search (WIMP search). The EXO experiment[6] is the Enriched Xenon Observatory in particle physics looking into detection of ``neutrino-less double beta decay''. It uses large amounts of xenon isotopically enriched in the isotope 136. A total 200-kg detector using liquid Xe is currently being installed at the Waste Isolation Pilot Plant (WIPP) near Carlsbad, New Mexico. “Many research and development efforts are underway for a ton-scale experiment, with the goal of probing new physics and the mass of the neutrino.” (EXO experiment). The CoGeNT[7] Dark Matter Experiment is a direct search of dark matter particles in a low-background germanium detector located at Soudan Underground Laboratory in Soudan, MN. The detector uses a single, 440-gram, high-purity germanium crystal cooled to liquid nitrogen temperatures in its measurements. The CoGeNT detector has very low energy threshold (~0.5 keV) so that it takes its advantage to search for nuclear recoil events from dark matter particles with relatively low mass. The detector is also built with very low background so that could recognize the signals very efficiently. Another advantage of the CoGent detector is that it senses only ionization charge from nuclear recoils and places limits on the mass and interaction cross-section of dark matter particles by excluding any candidate mass and cross-section pair that would result in a signal above the background of the detector.This experiment began collecting data in December 2009.

@@

\subsubsection{Super-Kamiokande}
The Super-Kamiokande experiment is a 22.5 kton water Cherenkov detector that looks at atmospheric neutrino oscillations. Their latest sterile neutrino analysis~\cite{SuperK} used a sterile vacuum fit to put limits on the mixing between $\nu_{\mu}$ and a sterile neutrino $\nu_4$, parameterized by $\left|U_{\mu 4}\right|^2 \approx \sin^2 \theta_{24}$, Figure~\ref{fig:SuperK}. Super-K can not measure $\Delta m^{2}_{41}$ in this analysis however, so when comparing to MiniBooNE the Super-K result is just a straight line. The Super-K result is is consistent with the MiniBooNE exclusion, providing verification on at least part of the MiniBooNE excluded region.

@@

\subsubsection{Daya Bay}
The Daya Bay experiment is a reactor antineutrino experiment with six liquid scintillator detectors located at different baselines from six 2.9 GW$_\text{th}$ nuclear reactors. It is able to make sterile neutrino measurements at smaller mass squared differences, $10^{−3} \text{ eV}^2  \lesssim \left|\Delta m^{2}_{41}\right| \lesssim 0.1 \text{ eV}^2$, than have been probed by other experiments to date~\cite{DayaBay}. While they have many different combinations of their detectors data sets, the Daya Bay exclusion limits mark out more of the small mass difference phase space than the combined LSND and KARMEN limits.

\begin{figure}[H]
 \centering
 \includegraphics[width=1\columnwidth]{../figures/daya1.pdf}
 \caption{Daya Bay sterile neutrino exclusion limits~\cite{DayaBay}.}
 \label{fig:DayaBay}
\end{figure}
